Grove: A Convergent Collaborative Structure-Editor Calculus

### 2020-07-21 grove-paper.tex
Updates from Overleaf

@@

Resolve by deleting one or the other or deleting both and adding replacement

(think about critiques re: diff)

(compare to what happens when there are conflicts in a VCS, you get 
diff markers inserted into files and the semantic editor services 
no longer understand the code)

@@

>>>>

Compare this to what happens when there are conflicts in a traditional,
line/diff-based version control system (e.g., \texttt{git}, \texttt{mercurial}, \texttt{svn}, etc.).
Those systems annotate files with difference markers (e.g., sequences of \texttt{<}, \texttt{>}, or \texttt{=})
when a merge conflict happens.
These show alternate versions versions of the code, and it is up to the user
to replace those alternates with the desired merged result.

Our tree-based model is similar in that it presents alternate versions
of the code, and it is up to the user to replace those alternates with the desired merged result.
Our model is different, in that merge conflicts in the line-based model
prevent some semantic editor services from running
that could continue to run in the tree-based model because
code inside and outside the conflict is still valid code.
It is just the point where they meet the poses a potential problem for editor services.
Another place our model is different
is that changes are explicit rather than being inferred.
Finally, in our model, since all changes are in terms of
the structure of the code rather than lines,
all changes respect that structure.
This is unlike the line-based model where there is no guarantee
that a merge conflict follows the structure of the code.
Finally, our model differs from the traditional model
in that we have explict add and remove actions
where the traditional model infers these from a differencing algorithm.

@@

@@

Before further exploring how to merge changes from multiple users,
we want to point out a common idiom

Traditional: no relation (and indent might change)
